\documentclass[10pt,xcolor={usenames},fleqn,serif]{beamer}

\hypersetup{pdfpagemode=FullScreen}

%% colors
\definecolor{bittersweet}{rgb}{1.0, 0.44, 0.37}
\definecolor{brilliantlavender}{rgb}{0.96, 0.73, 1.0}
\definecolor{antiquefuchsia}{rgb}{0.57, 0.36, 0.51}
\definecolor{violetw}{rgb}{0.93, 0.51, 0.93}
\definecolor{Veronica}{rgb}{0.63, 0.36, 0.94}
\definecolor{atomictangerine}{rgb}{1.0, 0.6, 0.4}
\definecolor{darkgray}{rgb}{0.66, 0.66, 0.66}
\definecolor{brightcerulean}{rgb}{0.11, 0.67, 0.84}
\definecolor{cadmiumorange}{rgb}{0.93, 0.53, 0.18}
\definecolor{ochre}{rgb}{0.8, 0.47, 0.13}
\definecolor{midnightblue}{rgb}{0.1, 0.1, 0.44}
\definecolor{lemon}{rgb}{1.0, 0.97, 0.0}
\definecolor{grey}{rgb}{0.7, 0.75, 0.71}
\definecolor{amber}{rgb}{1.0, 0.75, 0.0}
\definecolor{almond}{rgb}{0.94, 0.87, 0.8}
\definecolor{bf}{RGB}{88, 86, 88}
\definecolor{bb}{RGB}{177, 177, 177}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% importa pacchetti
\usepackage{usepkg}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Funzioni generali
\usepackage{functions}
%http://tex.stackexchange.com/questions/246/when-should-i-use-input-vs-include
\newcommand{\setmuskip}[2]{#1=#2\relax} %%problem usinig mu with calc (req by mathtools) loaded
\usepackage{beamersetup}
\usepackage{sources}
%\usepackage{length}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Funzioni per questo file main
\usepackage{mathOp}
\def\status{coazione}%ripeter
\def\keeptrying{coazione}
\usepackage{LocalF}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Let's get started
\begin{document}

\input{tikzdir}%%contain tikz files as filecontents

\addtobeamertemplate{block begin}{\setlength\abovedisplayskip{2pt}\setlength\belowdisplayskip{2pt}\setlength\abovedisplayshortskip{2pt}\setlength\belowdisplayshortskip{2pt}}

\addtobeamertemplate{block begin}{\vspace*{-3pt}}{}
\addtobeamertemplate{block end}{}{\vspace*{-3pt}}

\begin{frame}
  \titlepage
\end{frame}

% Section and subsections will appear in the presentation overview
% and table of contents.
%\frame{\tableofcontents[onlyparts]}

\begin{frame}[label={argomenti}]{Sistemi planetari: Sistema solare}
\tableofcontents[onlyparts]
\end{frame}

\begin{wordonframe}{Perch\'e studio queste cose?? Sviluppi; futuro.}

Osservazioni dischi protoplanetarii (radiazione corpo nero), trasferimento radiativo, ?struttura dischi e chemistry?

survei principali e loro bias: osservabili, risultati dei. Ensemble esopianeti:

\end{wordonframe}

\begin{wordonframe}{Dischi protoplanetarii}

\begin{itemize}
\item Formation evolution and dynamics of YSO.
Ch 2: Mass of dust and gas; Molecular emission and dust thermal emission.
Review of studies of continuus dust emission: williams cieza 11, testi 14, Andrews 15.
Intensity of dust emission depends on T and optical depth(projected surface density and opacity(Mie theory: particles absorbs wavelength of their size)),
dust opacity: $\kappa_{\nu}=\kappa_0(\frac{\nu}{\nu_0})\expy{\beta}$, normalizzazione e indice dipendono da composizione e dimensione della polvere; at millimeter wavelength $\nu\approx\SI{300}{\giga\hertz}$ the emission becomes optically thin for $\Sigma_d<\frac{1}{\kappa_{\nu}}\approx\SI{3}{\gram\per\squared\cm}$. For constant $T_d$: $M_d=\frac{F_{\nu}d^2}{\kappa_{\nu}B_{\nu}(T_d)}$ where d is distance os source.
Until self-gravity becomes important the distribution of particles size a follow $N(a)\propto a\expy{-p}$, $p\approx3.5$: total surface emitting area $\propto\int a^2N(a)\,da$ \'e dominata dalle particelle pi\'u piccole, mentre la massa $\propto\int a^3N(a)\,da$ \'e dominata da particelle pi\'u grandi (disks are easier to detect than planets)
Trends: higher mass stars have higher mass disks; disk masses decline rapidly with disk age (few Myr).

\end{itemize}

\end{wordonframe}

\part{Moti sistemi planetarii, struttura interna pianeti (emissione termica e non). Dischi di accrescimento.}\label{part:observables}
\input{observables}

\part{tecniche osservative}\label{part:tech}
\input{obstech}

\end{document}